\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving on Fixed Paths

### 2016-01-21 paper1.tex
a lot of cutting out figures

This information is used to choose the segment boundaries in the clustering step.
Any number of clustering algorithms may be used here, and prudent choice of segment boundaries is arguably one of the most critical pieces of trajectory planning process.
For the present example, we will choose a simple univariate heuristic which essentially identifies curves in the roadway.
Each time that $v_{m,k} < SL$ becomes true, a curve is beginning, and a segment boundary is drawn.
Each time that $v_{m,k} = SL$ is once again true, the current curve has ended, and another segment boundary is drawn.
Figure \ref{fig:course_highlight_turns} shows the result of this algorithm.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  \caption{
    Clustering output for a short path when using an algorithm which draws segment boundaries around curves.
    Portions in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
  }
  \label{fig:course_highlight_turns}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  \caption{
    Example of $v_m$ consolidation for simple univariate path clustering which corresponds the the path shown in Figure \ref{fig:course_highlight_turns}.
    The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling is shown in blue.
  }
  \label{fig:consolidation_speed_ceiling}
\end{figure}

@@

@@

@@

Several algorithms exist to find the optimal projection of the target vehicle's present kinematic state (position, velocity, and acceleration vectors) onto the path.
A simple approximation, which works well for the path shown in Figure~\ref{fig:course_highlight_turns} is to perpendicularly project the vehicle's position onto a series of lines running between each pair of adjacent points in the path (this will be referred to as a ``link'').
Projections which lie outside of the link's two constituent path points are snapped to that which is nearest.
The projection which is closest to the vehicle's actual position is then assumed to be the correct path projection $\mathbf{r}_p$.
Any number of modifications can be made using heading, velocity vectors, and previous information to allow this method to be extended to complex paths which overlap or self-intersect.

@@

Now the reference time corresponding to the vehicle's location $t_{veh}$ is needed to $v_{B,x}(t)$, $a_{B,x}(t)$, and $j_{B,x}(t)$.
Additionally, it is also needed to sample $s(t)$ at intervals ahead of the vehicle.
Since it is known that $s(t)$ is piecewise cubic, $t(s)$ may be approximated as cubic if a spline is being constructed from knots which have a very high resolution.
In this case, an $s(t)$ spline has already been created using the control points from the unified planning process described in Section~\ref{sec:unifiedsolution}, and it is now resampled at $\Delta t = 0.01 sec$.
This yields two vectors $s'$ and $t'$ which are then used to create a univariate cubic $t(s)$ spline.
Evaluating the $t(s_{veh})$ then yields the current reference time.

@@

Path Pre-processor conforms the path to planner assumptions. The Path Manager breaks up the
path at stop signs, decides when to stop, when to go and invokes the trajectory planner
as necessary.

There are two types of stops - Planned (PSTOP) and Reactive (RSTOP). At reactive stops
to pedestrians, the car may slow down and restart if the pedestrian leaves before the
car comes to a stop; otherwise the car would come to a stop and restarts once the 
pedestrian leaves.

The state of the car is represented by a State Machine as shown in figure \ref{fig:st}

@@

The assumption on our work is that there is a unique mapping from a time to s coordinate 
system. This mapping breaks down when we are stopped at a planned or reactive stop. 
The solution is to break the path into sub-paths, and plan and execute incrementally.
This is shown in Figures \ref{fig:segmentation} \ref{fig:stcur} and \ref{fig:scoord}.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{Segmentation of the path by path manager. The Trajectory generation is serially called on each segment colored differently. Need to update figure with stop signs????????????????}
  \label{fig:segmentation}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/course_highlighted_turns.png}
  \caption{Further characterization of green path shown in segmentation figure into straight and curved parts}
  \label{fig:stcur}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/1Dsegmentation.png}
  \caption{Showing the path projected onto the one dimensional s coordinate system}
  \label{fig:scoord}
\end{figure}

The algorithm is:
\begin{itemize}
\item Send first sub-path to trajectory planner
\item Wait until completed
\item Pause for fixed time
\item Send next sub-path to planner
\item Repeat until end of path
\end{itemize}

For unplanned, reactive stops  we need to slow down and stop. There are three scenarios:
\begin{enumerate}
\item Normal pedestrian → appears
\item Stopping pedestrian → moves
\item Stopped pedestrian leaves →
\end{enumerate}

@@

\begin{figure}[thpb]
\centering
  \subfigure[Normal mode]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL.png}}
\\
  \subfigure[Stopping for the pedestrian]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}}
\\
  \subfigure[Resuming after stop sign]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}}
  \caption{Reactive behavior to pedestrain}
  \label{fig:react}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/3phase_all_derivatives_SlowingDown.png}
  \caption{3 phase R stop}
  \label{fig:3phaserstop}
\end{figure}

@@

\section{Examples}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/FullStopSpec.png}
  \caption{Example 3 phase jerk profile}
  \label{fig:3phase}
\end{figure}

\section{2d to 1d conversion}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/PathProjection.png}
  \caption{Showing projection of current position of car shown by green triangle to s coordinate system}
  \label{fig:cartos}
\end{figure}
\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/PathProjectionSlice.png}
  \caption{car to s coord with additional points}
  \label{fig:cartos2}
\end{figure}
\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/s(t)_generic.png}
  \caption{Transformation from s coordinate system to time}
  \label{fig:stot}
\end{figure}

\section{Other Issues}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/LowResPathSample.png}
  \caption{Grid discretization issue}
  \label{fig:discretization}
\end{figure}
\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/linestring.png}
  \caption{Exaggerated view of path points which may have discontinuous curvature}
  \label{fig:disc}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/CircularCurvature.png}
  \caption{circular curvature}
  \label{fig:curv}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/speed_ceiling.png}
  \caption{Speed Ceiling}
  \label{fig:speedceil}
\end{figure}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}
  \caption{Reaction Response: Normal Mode}
  \label{fig:7phaseprofile}
\end{figure}

\section{Implementation}

\emph{How much should we say here?}

\section*{Acknowledgments}

Thanks...

>>>>

This information is used to choose the segment boundaries in the clustering step.
Any number of clustering algorithms may be used here, and prudent choice of segment boundaries is arguably one of the most critical pieces of trajectory planning process.
For the present example, we will choose a simple univariate heuristic which essentially identifies curves in the roadway.
Each time that $v_{m,k} < SL$ becomes true, a curve is beginning, and a segment boundary is drawn.
Each time that $v_{m,k} = SL$ is once again true, the current curve has ended, and another segment boundary is drawn.
Figure \ref{fig:1Dto2DandSegmentation} shows the result of this algorithm.

% \begin{figure}[thpb]
%   \centering
%   \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
%   \caption{
%     Clustering output for a short path when using an algorithm which draws segment boundaries around curves.
%     Portions in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
%   }
%   \label{fig:course_highlight_turns}
% \end{figure}

% \begin{figure}[thpb]
%   \centering
%   \includegraphics[width=1.0\columnwidth]{graphics/1Dsegmentation.png}
%   \caption{Showing the path projected onto the one dimensional s coordinate system}
%   \label{fig:scoord}
% \end{figure}

% \begin{figure}[thpb]
%   \centering
%   \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
%   \caption{
%     Example of $v_m$ consolidation for simple univariate path clustering which corresponds the the path shown in Figure \ref{fig:course_highlight_turns}.
%     The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
%     The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
%     The resultant speed ceiling is shown in blue.
%   }
%   \label{fig:consolidation_speed_ceiling}
% \end{figure}

\begin{figure}[thpb]
  \centering
  \subfigure[
    Clustering output for a short path when using an algorithm which draws segment boundaries around curves.
    Portions in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
  ]{
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    Showing the path projected onto the one dimensional s coordinate system
  ]{
    \includegraphics[width=1.0\columnwidth]{graphics/1Dsegmentation.png}
  }
  \\
  \subfigure[
    Example of $v_m$ consolidation for simple univariate path clustering which corresponds to the path shown above.
    The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling is shown in blue.
  ]{
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{\textbf{Cut down the subfigure captions and put it here!!!}}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

@@

@@

\subsection{2d to 1d conversion}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/PathProjection.png}
  \caption{Showing projection of current position of car shown by green triangle to s coordinate system}
  \label{fig:cartos}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/s(t)_generic.png}
  \caption{
    Transformation from s coordinate system to reference time.
    The figure depicts s(t) for a 3 phase jerk profile with positive forward acceleration.
  }
  \label{fig:stot}
\end{figure}

@@

Several algorithms exist to find the optimal projection of the target vehicle's present kinematic state (position, velocity, and acceleration vectors) onto the path.
A simple approximation, which works well for the path shown in Figure~\ref{fig:1Dto2DandSegmentation} is to perpendicularly project the vehicle's position onto a series of lines running between each pair of adjacent points in the path (this will be referred to as a ``link'').
Projections which lie outside of the link's two constituent path points are snapped to that which is nearest.
The projection which is closest to the vehicle's actual position is then assumed to be the correct path projection $\mathbf{r}_p$.
Any number of modifications can be made using heading, velocity vectors, and previous information to allow this method to be extended to complex paths which overlap or self-intersect.

@@

\subsection{Control Reference Signal} \label{sec:controlreferencesignal}

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/PathProjectionSlice.png}
  \caption{car to s coord with additional points}
  \label{fig:cartos2}
\end{figure}

Now the reference time corresponding to the vehicle's location $t_{veh}$ is needed to look up $v_{B,x}(t_{veh})$, $a_{B,x}(t_{veh})$, and $j_{B,x}(t_{veh})$.
Additionally, it is also needed to sample $s(t)$ at intervals ahead of the vehicle.
Since it is known that $s(t)$ is piecewise cubic, $t(s)$ may be approximated as cubic if a spline is being constructed from knots which have a very high resolution.
In this case, an $s(t)$ spline has already been created using the control points from the unified planning process described in Section~\ref{sec:unifiedsolution}, and it is now resampled at $\Delta t = 0.01 sec$.
This yields two vectors $s'$ and $t'$ which are then used to create a univariate cubic $t(s)$ spline.
Evaluating the $t(s_{veh})$ then yields the current reference time.

@@

Path Pre-processor conforms the path to planner assumptions.
The path manager breaks up the
path at stop signs, decides when to stop, when to go and invokes the trajectory planner
as necessary.

There are two types of stops: planned (PSTOP) and reactive (RSTOP).
At reactive stops
to pedestrians, the car may slow down and restart if the pedestrian leaves before the
car comes to a stop; otherwise the car would come to a stop and restarts once the 
pedestrian leaves.
The state of the car is represented by a State Machine as shown in figure \ref{fig:st}

@@

The assumption on our work is that there is a unique mapping from a time to s coordinate 
system.
This mapping breaks down when we are stopped at a planned or reactive stop, as there is now way to do a $t(s)$ when multiple reference time solutions exist for certain path positions.
The solution is to break the path into sub-paths, and plan and execute them incrementally as shown in Fig. \ref{fig:segmentation}.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{Segmentation of the path by path manager. The trajectory generation is serially called on each segment colored differently. \textbf{Need to update figure with stop signs????????????????}
  }
  \label{fig:segmentation}
\end{figure}

The procedure is:
\begin{itemize}
\item Send first sub-path to trajectory planner
\item Wait until completed
\item Pause for fixed time
\item Send next sub-path to planner
\item Repeat until end of path
\end{itemize}

For unplanned, reactive stops  we need to slow down and stop. 
There are three scenarios:
\begin{enumerate}
\item \emph{Normal}: pedestrian appears
\item \emph{Stopping}: pedestrian moves
\item \emph{Stopped}: pedestrian leaves
\end{enumerate}

@@

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RSTOP.png}}
  \\
  \subfigure[Resuming after stop sign]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_RESUME.png}}
  \caption{Reactive behavior to pedestrain}
  \label{fig:react}
\end{figure}

@@
